Figures

### 2020-02-11 figures/00_qa.Rmd
add manual vs bathy panels to makefile

```{r lgnemanual-bathy-meandepth}
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)
dt_sub <- dt %>%
  dplyr::filter(
    lagos_effort %in% c("LAGOSNE", "bathymetry", "manual") &
    !is.na(lake_meandepth_m)) %>%
  dplyr::select(lagoslakeid, lake_state, lagos_effort, lake_meandepth_m) %>%
  tidyr::pivot_wider(names_from = lagos_effort, 
                     values_from = c(lake_meandepth_m)) %>%
  dplyr::filter(!is.na(bathymetry)) %>%
  mutate(combined = coalesce(manual, LAGOSNE)) %>%
  dplyr::filter(!is.na(combined))

(gg <- ggplot(data = dplyr::filter(dt_sub, !(lake_state %in% c("ME", "NH")))) +
  geom_text(aes(x = bathymetry, y = combined, color = lake_state, 
                 label = lagoslakeid)) +
  geom_abline(aes(intercept = 0, slope = 1)))

# plotly::ggplotly(gg)
```

>>>>

```{r lgnemanual-vs-bathy-depth, fig.height=3}
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)

dt_sub <- dt %>%
  dplyr::filter(
    lagos_effort %in% c("LAGOSNE", "bathymetry", "manual") &
    !is.na(lake_meandepth_m)) %>%
  dplyr::select(lagoslakeid, lake_state, lagos_effort, lake_meandepth_m) %>%
  tidyr::pivot_wider(names_from = lagos_effort, 
                     values_from = c(lake_meandepth_m)) %>%
  dplyr::filter(!is.na(bathymetry)) %>%
  mutate(combined = coalesce(manual, LAGOSNE)) %>%
  dplyr::filter(!is.na(combined))

gg_mean <- ggplot() +
  geom_point(data = dt_sub, 
             aes(x = bathymetry, y = combined, color = lake_state), 
             alpha = 0.6) +
  geom_point(data = dplyr::filter(dt_sub, !(lake_state %in% c("ME"))), 
             aes(x = bathymetry, y = combined, color = lake_state)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Calculated (m)") + ylab("Reported (m)") +
  ggtitle("Mean Depth")

# plotly::ggplotly(gg)

dt_sub <- dt %>%
  dplyr::filter(
    lagos_effort %in% c("LAGOSNE", "bathymetry", "manual") &
    !is.na(lake_maxdepth_m) &
    !(lagoslakeid %in% c(456169))) %>% # remove llids with duplicate manual depth
  dplyr::select(lagoslakeid, lake_state, lagos_effort, lake_maxdepth_m) %>%
  tidyr::pivot_wider(names_from = lagos_effort, 
                     values_from = c(lake_maxdepth_m)) %>%
  dplyr::filter(!is.na(bathymetry)) %>%
  mutate(combined = coalesce(manual, LAGOSNE)) %>%
  dplyr::filter(!is.na(combined))

gg_max <- ggplot(data = dt_sub) +
  # geom_text(aes(x = bathymetry, y = combined, color = lake_state, 
  #                label = lagoslakeid)) +
  geom_point(aes(x = bathymetry, y = combined, color = lake_state)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Calculated (m)") + ylab("Reported (m)") +
  ggtitle("Max Depth")

cowplot::plot_grid(gg_max + theme(legend.position = "none"), 
                   gg_mean + theme(axis.title.y = element_blank()), 
                   rel_widths = c(0.7, 1))
```

### 2020-02-11 manuscript/figures.Rmd
rm programs tally
add manual vs bathy panels to makefile

@@

![Lake shape caption](../figures/lake_shape.pdf){width=100%}

@@

```{r 01_programs_tally, fig.cap = "Number of programs by categories.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_programs_tally-1.pdf")
```

>>>>

![Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right)](../figures/lake_shape.pdf){width=100%}

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported max depth and max depth calculated from bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```

@@

@@
